\PassOptionsToPackage{dvipsnames}{xcolor}

\documentclass[10pt,a4paper]{altacv}

% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}

% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{Navy}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
%% sample.bib contains your publications
\addbibresource{biblio.bib}

\usepackage[colorlinks]{hyperref}

\usepackage{xstring}
\noexpandarg\exploregroups
\makeatletter
\let\orig@blx@bbl@entry\blx@bbl@entry
\def\blx@bbl@entry#1\endentry{%
	\StrSubstitute{#1}{Gabrieli}{\textbf{Gabrieli}}[\Result]%
	\expandafter\orig@blx@bbl@entry\Result\endentry}
\makeatother


\begin{document}
    
	\begin{fullwidth}
    \hspace*{\fill} {\footnotesize Last updated on \today}
	\end{fullwidth}
	
	\name{Giulio Gabrieli}
	\tagline{Ph.D. Candidate}
	\personalinfo{%
		% Not all of these are required!
		% You can add your own with \printinfo{symbol}{detail}
		
		\email{\href{mailto:gack94@gmail.com}{gack94@gmail.com}}
		\email{giulio001@e.ntu.edu.sg}
	}
	
	%% Make the header extend all the way to the right, if you want. 
	\begin{fullwidth}
		\makecvheader
	\end{fullwidth}
	
	%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
	\AtBeginEnvironment{itemize}{\small}
	
	
	%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
	%% You can always just use \marginpar{...} if you do
	%% not need to align the top of the contents to any
	%% \cvsection title in the "main" bar.
	\cvsection[page1sidebar]{Education}
	
	\divider
	\cvevent{\textbf{Ph.D. in Psychology}}{Nanyang Technological University}{January 2019 -- Ongoing}{Singapore, Singapore}{}{}
	School of Social Sciences (SSS)\\
	\textbf{CGPA:} 4.83 / 5.0\\
	\textbf{GPA:} 3.90 / 4.0
	
	\divider
	
	\cvevent{MSc in Human-Computer Interaction}{University of Trento}{September 2016 - July 2018}{Trento, Italy}{}{}
	Department of Psychology and Cognitive Science (DIPSCO)\\
	Department of Information Engineering and Computer Science (DISI)\\
	\textbf{GPA:} 3.64 / 4.0\\
	\textbf{110/110 with honors}\\
	
	\divider
	
	\cvevent{BSc in Interfaces and Communication Technology}{University of Trento}{September 2013 - September 2016}{Trento, Italy}{}{}
	Department of Psychology and Cognitive Science (DIPSCO)\\
	\textbf{GPA:} 3.63 / 4.0\\
	\textbf{110/110 with honors}\\
	
	\divider
	
	\cvevent{Erasmus+}{Nagasaki University}{October 2016 - March 2017}{Nagasaki, Japan}{}{}
	Graduate School of Biomedical Sciences
	
	\divider
	
	\cvevent{Summer Research Internship}{Nanyang Technological University}{June 2016 - July 2016}{Singapore, Singapore}{}{}
	School of Humanities and Social Sciences
	
	
	\divider
	
	\cvevent{High School Diploma in Chemistry with specialization in Food Technology}{I.T.I.S. G. Ferraris}{September 2008 - June 2013}{Verona, Italy}{}{}
	
	\medskip
	
	\newpage
	\cvsection[page2sidebar]{Experience}
	
	\cvevent{Ph.D. Candidate}{Social and Affective Neuroscience Lab}{January 2019 - Ongoing}{Nanyang Technological University}{Signal processing (ECG, EDA, EMG, EEG, fNIRS, fMRI, infant cry), Experimental design \& Data collection, Big Data Analysis, Manuscript preparation}{}
	
	\divider
	
	\cvevent{Intern}{Affiliative Behaviour and Physiology Lab}{June 2015 - December 2018}{University of Trento}{Signal processing (ECG, EDA, EMG, EEG, infant cry), Experimental design \& Data collection, Manuscript preparation}{}
	
	\divider
	
	\cvevent{Data Entry}{Hellas Verona F.C. s.p.a}{June 2014 - December 2018}{Verona, Italy}{IT support and digital tickets management.}{}
	
	\divider
	
	\cvevent{Research assistant}{Affiliative Behaviour and Physiology Lab}{June 2018 - September 2018}{University of Trento}{Data analysis, manuscript preparation, speaker at scientific meetings.}{}
	
	\divider
	
	\cvevent{Scientific Meeting Organization}{University of Trento}{June 2017 - August 2017}{University of Trento}{Website design and IT support for 13th International Infant Cry Workshop.}{}
	
	\begin{fullwidth}
	
	\cvsection{Teaching Experience}
	
    \cvevent{Teaching Assistant}{HP2700: Abnormal Psychology}{2020-2021}{Nanyang Technological University, Singapore}
    
    \divider
    
    \cvevent{Teaching Assistant}{HP4222-7237: The Neuroscience of Love
}{2019-2020}{Nanyang Technological University, Singapore} 
    
    \divider
    
    \cvevent{Teaching Assistant}{HP4021: Laboratory in Human and Animal Neuroscience}{2019-2020}{Nanyang Technological University, Singapore}
    
		\newpage
		\cvsection[]{Publications}
		
		\nocite{*}
		
		\def\yrlist{2021,...,2018}
		
		\defbibfilter{papers}{
			type=article or
			type=incollection or
			type=inproceedings or 
			type=inbook
		}
		
% 		\defbibfilter{talks}{
% 			type=presentation
% 		}
		
		\foreach \yr in \yrlist{
			\defbibcheck{publicationInthisYear}{
				\ifnumequal{\thefield{year}}{\yr}{}{\skipentry}
			}
			\printbibliography[check=publicationInthisYear, title=\yr,filter=papers]{}
		}
        
        % \printbibliography[filter=papers]{}
		
		\cvsection[]{Talks and Posters}
		
% 		\def\yrlist{2021,...,2016}
% 		\foreach \yr in \yrlist{
% 			\defbibcheck{publicationInthisYear}{
% 				\ifnumequal{\thefield{year}}{\yr}{}{\skipentry}
% 			}
% 			\printbibliography[check=publicationInthisYear, title=\yr, filter=talks]{}
% 		}
		
% 		\printbibliography[filter=talks]{}

\begin{itemize}
\subsection*{2021}
\item  \textbf{Gabrieli, G.}, Lim, Y. Y., \& Esposito, G. (2021, June 23–26). Effects of social distancing on the strength halo effect: Doesattachment style matter?5th international conference of the European Society for Cognitive and AffectiveNeuroscience (ESCAN), Virtual.
 \item Ng, X., \textbf{Gabrieli, G.}, Azhari, A., Neoh, M. J. Y., \& Esposito, G. (2021, June 23–26). Baby don’t cry. measuring theempathetic response towards infant cries in a singaporean context. 5th international conference of the EuropeanSociety for Cognitive and Affective Neuroscience (ESCAN), Virtual.
 \item Bizzego, A., Lim, M., Schiavon, G., Setoh, P., \textbf{Gabrieli, G.}, Dimitriou, D., \& Esposito, G. (2020, April 7–9). Parentingand child disability in low‐ and middle‐income countries: Data‐driven approaches on open big data. Society for Researchin Child Development Biennial Meeting, Virtual.
 \item  \textbf{Gabrieli, G.}, Bornstein, M. H., Manian, N., \& Esposito, G. (2020, April 7–9). Using infants’ cry vocalizations to assesspost‐partum depression in their mothers. Society for Research in Child Development Biennial Meeting, Virtual.
 \item Carollo, A., Bizzego, A., \textbf{Gabrieli, G.}, Wong, K. K. Y., Raine, A., \& Esposito, G. (2021, February 2). Perceived lonelinessand lockdown duration: Using artificial intelligence to uncover patterns in covid‐19 data. President’s Forum onSoutheast and South Asia and Taiwan Universities, Virtual.
 \item Carollo, A., Bonassi, A., Cataldo, I., \textbf{Gabrieli, G.}, Lepri, B., \& Esposito, G. (2021, February 19–20). The effect ofavoidant attachment with the partner on the number of followed users on instagram: A gxe study. European Conferenceon Digital Psychology, Milan, Italy.
 
\subsection*{2020}
 \item Carollo, A., Bizzego, A., \textbf{Gabrieli, G.}, Wong, K., Raine, A., \& Esposito, G. (2020, October 31–November 7). I’m alonebut not lonely: Investigating the u‐shaped pattern of perceived loneliness during the covid‐19 pandemic in the unitedkingdom and greece. Society of Behavioural Health Virtual Scientific Meeting, Virtual.
 \item  \textbf{Gabrieli, G.} (2020, September 11). An analysis of the generalizability and stability of the halo effect. School of SocialSciences ‐ Graduate Students Club’s Brownbag Seminar, Singapore, Singapore.
 \item Bonassi, A., Cataldo, I., \textbf{Gabrieli, G.}, Nee Foo, J., Lepri, B., \& Esposito, G. (2020, September 12–15). Serotonintransporter gene polymorphisms and confidence in adult relationships affect the number of followed people on instagram.33rd Congress of the European College of Neuropsychopharmacology, Virtual.
 \item Caruso, A., \textbf{Gabrieli, G.}, Fulceri, F., Micai, M., Esposito, G., Network, N., \& Scattoni, M. (2020, May 20–21). Acousticfeatures of cry from birth as early markers of neurodevelopmental disorders. Behavioural Measures of LanguageAcquisition and language processing in typical and atypical populations, Venice, Italy.
 \item Bonassi, A., Cataldo, I., \textbf{Gabrieli, G.}, Lepri, B., \& Esposito, G. (2020, February 7–8). Genetic predispositions and earlyparent‐child relationship are related to instagram behaviour. Cognitive Science Arena (CSA), Brixen, Italy.
 \item Gobbi, P., Bonassi, A., Cataldo, I., \textbf{Gabrieli, G.}, Lepri, B., \& Esposito, G. (2020, February 7–8). Exploring sociableattitudes in facebook: A gene‐environment investigation. Cognitive Science Arena (CSA), Brixen, Italy.
 
\subsection*{2019}
 \item Bizzego, A., \textbf{Gabrieli, G.}, Bornstein, M. H., Deater‐Deckard, K., Putnick, D. L., Lansford, J. E., Bradley, R. H., Costa, M.,\& Esposito, G. (2019a, December 9–12). Child mortality in low‐ and middle‐income countries: A transdisciplinary studyusing artificial intelligence. 3rd International Developmental Pediatrics Association Congress ‐ Transdisciplinaryinterventions: Idea in Action, Manila, Philippines.
 \item Bonassi, A., Cataldo, I., \textbf{Gabrieli, G.}, Lepri, B., \& Esposito, G. (2019, December 8–14). Genetic factors and earlyparent‐infant interactions shape instagram users’ social behaviour. Federation of European Neuroscience Societies(FENS) Hertie Winter School, Obergurgl, Austria.
 \item Kamburova, H., Kumar, R., Gao, F., \& \textbf{Gabrieli, G.} (2019, December 5). Open access in the asia‐pacific countries: A q\&awith academics. Researcher App Webinair.
 \item Goh, G., S. N. Gabrieli, \& Koh, W. (2019, December 5). Open data and materials. Singapore ReproducibiliTea,Singapore, Singapore.
 \item  \textbf{Gabrieli, G.} (2019a, November 21). Reproducibility now: Why many studies are not reproducible?SingaporeReproducibiliTea, Singapore, Singapore.
 \item  \textbf{Gabrieli, G.} (2019b, September 29). Using artificial intelligence to fight child mortality. Healthcare Tech ‐ La Kopi @Google Developer Space, Singapore, Singapore.
 \item Bizzego, A., \textbf{Gabrieli, G.}, Azhari, A., Setoh, P., \& Esposito, G. (2019, June 12–14). Computational methods for theassessment of empathic synchrony. Italian Workshop on Neural Networks (WIRN), Vietri sul Mare, Italy.
 \item Azhari, A., Leck, W. Q., \textbf{Gabrieli, G.}, Bizzego, A., Rigo, P., Setoh, P., Bornstein, M. H., \& Esposito, G. (2019, May 2–4). Parenting stress undermines mother‐child interbrain synchrony. Social \& Affective Neuroscience Society (SANS),Miami, United States.
 \item Bizzego, A., \textbf{Gabrieli, G.}, Bornstein, M. H., Deater‐Deckard, K., Putnick, D. L., Lansford, J. E., Bradley, R. H., Costa, M.,\& Esposito, G. (2019b, April 8–10). Adapting the maqc‐dap to the unicef mics dataset to predict child mortality in low‐and middle‐income countries. 3rd Annual MAQC Society Conference, Trento, Italy.
 \item  \textbf{Gabrieli, G.} (2019c, March 29). Predicting child mortality in low‐ and middle‐income countries: A big data approach. “3Minute Thesis” Competition, Singapore, Singapore.
 \item  \textbf{Gabrieli, G.}, Leck, W. Q., Bizzego, A., \& Esposito, G. (2019, March 23–26). Are praat’s default settings optimal forinfant cry analysis?Linux Audio Conference, Stanford, United States.
 \item Qing, L. W., Azhari, A., Bizzego, A., \textbf{Gabrieli, G.}, \& Esposito, G. (2019, August 8). Mother‐child brain synchrony: Aunique dyadic coupling. International Symposium on Cognition and Neuroscience (ISCN), Singapore, Singapore.

\section*{2018}
 \item  \textbf{Gabrieli, G.}, Truzzi, A., Rigo, P., Onnis, L., \& Esposito, G. (2018, July 19–22). Promoting empathy with rhymes: Effectsof poetry exposure on physiological arousal and empathic trait. European Society for Cognitive and AffectiveNeuroscience (ESCAN), Leiden, The Netherlands.
 \item  \textbf{Gabrieli, G.}, Azhari, A., \& Esposito, G. (2018, June 13–15). Pysiology: A python package for physiological featureextraction. Italian Workshop on Neural Networks (WIRN), Vietri sul Mare, Italy.
 \item  \textbf{Gabrieli, G.}, \& Esposito, G. (2018a, May 3–5). Neuroaesthetics and web design: How expertise shapes our perception ofweb pages. Concepts, Actions and Objects (CAOS), Rovereto, Italy.
 \item Venturoso, L., \textbf{Gabrieli, G.}, Truzzi, A., \& Esposito, G. (2018, May 3–5).“isn’t it lovely?”: Gender differences in responseto babies and adults faces of different ethnic groups. Concepts, Actions and Objects (CAOS), Rovereto, Italy.
 \item  \textbf{Gabrieli, G.}, Esposito, G., Setoh, P., Vil, S., \& Truzzi, A. (2018a, April 4–5). Love patterns: A machine learning approachto the study of individuals’ perception of romantic interactions in ongoing and past relationships. Consortium ofEuropean Research on Emotion, Glasgow, Scotland.
 \item  \textbf{Gabrieli, G.}, Esposito, G., Setoh, P., Vil, S., \& Truzzi, A. (2018b, February 23–24). A machine learning approach to thestudy of individuals’ perception of romantic relationships. Cognitive Scienc e Arena (CSA), Brixen, Italy.
 \item Ghilardi, T., Bonassi, A., \textbf{Gabrieli, G.}, Doi, H., Shinohara, K., \& Esposito, G. (2018, February 23–24). The influence ofethnicity in the recognition ability of emotional faces and voices. Cognitive Scienc e Arena (CSA), Brixen, Italy.
 \item  \textbf{Gabrieli, G.}, Scapin, G., Panzariello, S., \& Esposito, G. (2017, July 6–8). Analysis of available methods for fundamentalfrequency estimation applied to the infant cry. 13th International Infant Cry Workshop, Rovereto, Italy.
 \item  \textbf{Gabrieli, G.} (2017, June 16). Bci 101 ‐ introduction to brain computer interfaces. 13thSpeck and Tech, Trento, Italy.
 \item  \textbf{Gabrieli, G.}, Lim, M., Bolcato, C., Truzzi, A., Rigo, P., Onnis, L., \& Esposito, G. (2017, March 16–18). Reading poetryincreases adults’ empathetic traits and moderated physiological arousal. Social and affective Neuroscience Society(SANS), Los Angeles, United States.
 \item  \textbf{Gabrieli, G.}, \& Esposito, G. (2018b, August 30–September 2). Neuroaesthetic of websites: Evaluating the impact ofexpertise and exposure to website on aesthetic judgment. International Association of Empirical Aesthetics Congress(IAEA), Toronto, Canada.
 \item  \textbf{Gabrieli, G.} (2016). The dynamics of love, Singapore, Singapore
\end{itemize}
	
		\cvsection[]{Grants}
		
		\begin{itemize}
			\item Singapore's National Super Computing Centre January 2020 Cycle, Project: \textit{Computational study of Child Development in Low Resource Contexts} (Project ID: 12001609)
		\end{itemize}
		
		\cvsection[]{Thesis}
		\begin{itemize}
			\item \textbf{Gabrieli G.}, Esposito G. (2018), Using users' physiological response to predict aesthetic experience of websites, Master Degree in Human-Computer Interaction, University of Trento (Italy) [\href{http://www5.unitn.it/Biblioteca/it/Web/RichiestaConsultazioneTesi/364090}{PDF@UNITN}]
			
			\item \textbf{Gabrieli G.}, Esposito G. (2016), Development of a Web platform for graphical data collection and analysis, Bachelor Degree in Interfaces and Communication Technology, University of Trento (Italy) 
		\end{itemize}
		
		To get access to the above works, please \href{mailto:gack94@gmail.com}{contact me.}
		
		\cvsection[]{Software and Tools}
		\begin{itemize}
			\item \textbf{Pysiology} - A Python package for physyological's signals processing  [\href{https://github.com/Gabrock94/Pysiology}{GitHub}] [\href{https://pypi.org/project/pysiology/}{PyPI}] [\href{https://pysiology.rtfd.io}{Documentation}] 
			
			\item \textbf{PrettyWebsite} -  Websites' aesthetic analysis in Python  [\href{https://github.com/Gabrock94/PrettyWebsite}{GitHub}] [\href{https://pypi.org/project/prettywebsite/0.0.3/}{PyPI}] [\href{https://prettywebsite.readthedocs.io/en/latest/?badge=latest}{Documentation}] 
			
			\item \textbf{FNIRSQC} -  fNIRS Quality Control using Deep Learning Platform  [\href{https://socialaffectiveneuroscience.com/fnirsqc/}{Website}]
			
			\item \textbf{bfp}: a simple template to develop PWA with Firebase and Bootstrap.  [\href{https://github.com/Gabrock94/bfp}{GitHub}]
			
			\item \textbf{pyEasyTrend} - The simplest way to perform trend analysis in Python [\href{https://github.com/Gabrock94/pyEasyTrend}{GitHub}] [\href{https://pypi.org/project/pyEasyTrend/}{PyPI}] [\href{https://pyeasytrend.readthedocs.io}{Documentation}] 
		\end{itemize}
		
		\cvsection[]{Datasets}
% 		\printbibliography[type=dataset]
% 		\def\yrlist{2021,...,2019}
% 		\foreach \yr in \yrlist{
% 			\defbibcheck{publicationInthisYear}{
% 				\ifnumequal{\thefield{year}}{\yr}{}{\skipentry}
% 			}
% 			\printbibliography[check=publicationInthisYear, title=\yr, type=dataset]
% 		}
		
		\cvsection[]{Preregistrations}
		\begin{itemize}
		    \item \textbf{Gabrieli, G.}, \& Esposito, G. (2020, December 10). Aesthetics vs Liking: Taxonomy of the Halo Effect. \href{https://doi.org/10.17605/OSF.IO/ABVWC}{https://doi.org/10.17605/OSF.IO/ABVWC}
            \item \textbf{Gabrieli, G.}, Qi, S. N. S., Du Lim, N., \& Esposito, G.(2020, September 10). Halo Effect (Aesthetics x Trustworthiness) on objects on which Human Faces are displayed  (ATMs, short-term vs. long-term). \href{https://doi.org/10.17605/OSF.IO/BNPQZ}{https://doi.org/10.17605/OSF.IO/BNPQZ}
            
            \item \textbf{Gabrieli, G.}, Lim, Y. Y., Du Lim, N., \& Esposito, G. (2020, August 30). Halo Effect  (Aesthetics x Trustworthiness) of Human Faces under Priming conditions. \href{https://doi.org/10.17605/OSF.IO/RZDXH}{https://doi.org/10.17605/OSF.IO/RZDXH}
            
            \item \textbf{Gabrieli, G.}, \& Peipei, S. (2020, June 17). Automatic identification of toddlers’ pupillometry (fixation time) measures signal quality. Retrieved from \href{https://doi.org/10.17605/OSF.IO/ET95X}{https://doi.org/10.17605/OSF.IO/ET95X}
            
            \item Carollo A., Bizzego A., \textbf{Gabrieli G.}, Esposito G. (2020 May, 26) Artificial intelligence for the study of changes in human behavior during the COVID-19 outbreak. Retrieved from \href{https://osf.io/8xtbq/}{https://osf.io/8xtbq/}
            
            \item \textbf{Gabrieli, G.}, Esposito, G., Goh, R., \& Gualco, C. (2020, May 13). Effects of priming on faces' Aesthetic, Trustworthiness, Closeness, and Concern. Retrieved from \href{https://doi.org/10.17605/OSF.IO/YDS8B}{https://doi.org/10.17605/OSF.IO/YDS8B}
            
            \item \textbf{Gabrieli, G.}, Esposito, G., Goh, R., \& Gualco, C. (2020, May 13). Changes in individias' trusthworthiness judgments toward Asian faces following the 2019–20 coronavirus outbreak. Retrieved from \href{https://osf.io/hqj8n}{https://osf.io/hqj8n}
            
            \item Bonassi A., Carollo A., Cataldo I., \textbf{Gabrieli G.}, Lepri B., \& Esposito G. (2020, February 26). A potential interaction between genetic predispositions and adult attachment patterns on Facebook behaviour. Retrieved from \href{https://osf.io/egsc7}{https://osf.io/egsc7}
            
            \item Bonassi A., Cataldo I., \textbf{Gabrieli G.}, Lepri B., \& Esposito G. (2020, February 26). The interplay between Oxytocin Receptor Gene and adult close relationship on Instagram behaviour. Retrieved from \href{https://osf.io/t78fu}{https://osf.io/t78fu}
            
            \item Bonassi, A., Cataldo, I., \textbf{Gabrieli, G.}, Lepri, B., \& Esposito, G. (2019, November 20). Oxytocin Receptor Gene polymorphism and early parental bonding interact in modulating Facebook social behaviour. Retrieved from \href{https://osf.io/xudkn}{https://osf.io/xudkn}
            
            \item \textbf{Gabrieli, G.}, Esposito, G., \& Goh, R. (2019, October 30). Faces' Aesthetic and Trustworthiness. Retrieved from \href{https://osf.io/acpm7}{osf.io/acpm7}
            
            \item \textbf{Gabrieli G.}, Goh R., Esposito G., \& Carollo A. (2019, October 13). Baby faces and Media. Retrieved from \href{https://osf.io/4n6mh}{osf.io/4n6mh} 
            
            \item Bonassi, A., Cataldo, I., \textbf{Gabrieli, G}., Lepri, B., \& Esposito, G. (2019, October 4). Oxytocin Receptor Gene and early parental bonding interact in shaping Instagram social behaviour. Retrieved from \href{https://osf.io/j9nqc}{https://osf.io/j9nqc} 
	
	\end{itemize}
		
		\cvsection[]{Peer Reviewing}
		\begin{itemize}
			\item Research in Developmental Disabilities (6)
			\item Behavior Research Methods (2)
			\item Infant Behavior and Development (2)
			\item Scientific Data (1)
			\item Smart Innovation, Systems and Technologies (1)
			\item Frontiers in Psychology (1)
			\item Swiss National Science Foundation (1)
		\end{itemize}
		
		\divider
		
		\cvsection{Non-Formal Education}
		
		\cvevent{Designing an Infographic}{Linkedin Learn}{February 2021}{Online}{}{}
		
		\cvevent{Learning Data Visualization}{National Association of State Boards of Accountancy (NASBA) | Linkedin Learn}{February 2021}{Online}{}{}
		
		\cvevent{Learning Data Science: Tell Stories With Data}{National Association of State Boards of Accountancy (NASBA) | Linkedin Learn}{February 2021}{Online}{}{}
		
		\cvevent{NIRx Virtual fNIRs Training Course}{NIRx}{January 25 - February 5 2021}{Online}
		
		\cvevent{HTML5 Game Development with Phaser}{Linkedin Learn}{November 2020}{Online}{}{}
		
		\cvevent{Cloud OnBoard: GCP Fundamentals Series}{Google Cloud}{24–26 March 2020}{Online}{}{}
		
		\cvevent{MATLAB Onramp}{MathWorks}{January 2019}{Online}{}{}
		
	\end{fullwidth}
	
\end{document}
